### 2015-02-22 appendices.tex
switched references to biblatex

\subsection{}

>>>>

\section{ADDITIONAL SDLC DATA NEEDS}

    \subsection{ESTIMATION}

    \begin{itemize}
    \item Change to Database Structure  
    \item Modify Database Data    
    \item Create a New Database, number of new databases  
    \item Server Configuration Changes Required   
    \item New Servers Required   
    \item Number of Team Members Involved  
    \item Number of (sub)Systems Involved  
    \item Estimation Date
    \item Number of Days Allowed
    \item List of Other Attributes
    \item Number of Screens Involved 
    \item Actual Value (hours, days, dollars) 
    \end{itemize}

    \begin{description}
        \item[Estimated Dev Hours] - 
            The number of development hours estimated for a 
            project, this is just developer hours
        \item[Estimated Doc Hours] - 
            The number of documentation hours estimated for a project
        \item[Estimated Test Hours] - 
            The number of testing hours estimated for a project
        \item[Estimated Deployment Hours] - 
            The number of estimated hours required to 
            deploy the project
    \end{description}

    \subsection{REQUIREMENTS}
    List of: 
    \begin{description}
      \item[Title] 
      \item[Descrition]
      \item[author]
      \item[projectID]
      \item[date]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{MAINTENANCE (DEFECTS)}
    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[description]
      \item[date Entered]
      \item[Date fixed]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{TESTING}

    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[title]
      \item[description]
      \item[author]
      \item[Date Started]
      \item[Date Executed]
      \item[Status (Pending, pass, fail)]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{DEVELOPMENT}

    List of Coding Tasks:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[List of Files]
      \item[author]
      \item[Date Started]
      \item[Completion Date]
      \item[Number of Unit Tests]
      \item[Lines of Code]
      \item[Others] See \cite{Jones2009, Jones2012, Rubin2007, Snipes2013}
    \end{description}

    \subsection{IMPLEMENTATION}

    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[date Entered]
      \item[Date Scheduled]
      \item[Date Executed]
      \item[Ordering/Prerequisites]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

### 2015-02-22 paper_40_mpi.tex
switched references to biblatex

                Once all the $\Delta_i$'s have been determined, a distribution must
                be fit to the data.  The exact distribution is needed for the Cumulative
                Distribution Function (C.D.F.).  The C.D.F. will be transformed to create
                the schedule score for MPI. Since all C.D.F. functions fall within the
                range $[0,1]$, the function needs to be shifted to center around 0, and then
                doubled to fill the desired range of $[-1,1]$. Thus the MPI schedule score
                for each project becomes the following.

>>>>

                Once all the $\Delta_i$'s have been determined, a distribution must
                be fit to the data. There are several techniques for testing the fit
                of a distribution: histograms, chi-square, Kolmogorov-Smirnov, Shapiro-Wilk,
                or Anderson-Darling \cite{Damodaran2015,Kutner2003}.
                The distribution is needed for the Cumulative
                Distribution Function (C.D.F.). The C.D.F. maps the values
                to a percentile rank within the distribution \cite{Downey2011}.
                The C.D.F. will be transformed to create
                the schedule score for MPI. Since all C.D.F. functions fall within the
                range $[0,1]$, the function needs to be shifted to center around 0, and then
                doubled to fill the desired range of $[-1,1]$. Thus the MPI schedule score
                for each project becomes the following.
